Budgeted Reinforcement Learning\\in Continuous State Space

### 2019-12-01 paper/talk/edouard/main.tex
Update talk

\section{Setting}
\frame{\sectionpage}

\begin{frame}{Motivation}

\begin{alertblock}{Conflicting Objectives}
Single scalar reward to represent multiple contradictory aspects (task completion vs safety)

No explicit control over the tradeoffs
\end{alertblock}

Examples?
\end{frame}

\begin{frame}{Examples}
\begin{alertblock}{Dialogue systems}
A slot-filling problem: the agent fills a form by asking the user each slot. It can either:
\begin{itemize}
	\item ask to answer using {\green voice} {\green (safe/slow)};
	\item ask to answer with a {\red numeric pad} {\red (unsafe/fast)}.
\end{itemize}
\end{alertblock}

\begin{alertblock}{Autonomous Driving}
The agent is driving on a two-way road with a car in front of it,
\begin{itemize}
\item it can {\green stay behind} {\green (safe/slow)};
\item it can {\red overtake} {\red (unsafe/fast)}.
\end{itemize}
\begin{center}
\href{https://budgeted-rl.github.io/assets/highway-neutral.gif}{\includegraphics[width=0.5\linewidth]{img/highway_env}}
\end{center}
\end{alertblock}
\end{frame}

@@

@@

\begin{frame}{Augmented Settings}
Budgeted policies $\pi$
\begin{itemize}
	\item Take a budget $\beta$ as an additional input
	\item Output a next budget $\beta'$ 
	\item $\pi:\underbrace{(s,\beta)}_{\os} \rightarrow \underbrace{(a,\beta')}_{\oa}$
\end{itemize}

@@

\begin{frame}{More scaling}

>>>>

\section{Motivation and Setting}
\frame{\sectionpage}

\begin{frame}{Learning to act}
\begin{alertblock}{Optimal Decision-Making}
	Which action $a_t$ should we choose in state $s_t$ to maximise a cumulative reward $R$?
	\begin{equation*}
	\max_\pi \expectedvalueover{a_t\sim\pi(a_t|s_t)} \left[\sum_{t=0}^\infty \gamma^t R(s_t, a_t)\right]
	\end{equation*}
\end{alertblock}

\pause
\begin{itemize}
	\item[\green \checkmark] A very general formulation
	\item[\green \checkmark]<2|only@2> Widely used in the industry
	\item[\red \xmark]<3-4> {\red \textbf{Not}} widely used in the industry
	\only<4>{\begin{itemize}
			\item Sample efficiency
			\item Trial and error
			\item Unpredictable behaviour
	\end{itemize}}
\end{itemize}
\end{frame}

\begin{frame}{Limitation of Reinforcement Learning}

Reinforcement learning relies on a \alert{single reward function $R$}
\begin{itemize}[<+->]
	\item[\green \checkmark] A convenient formulation, but;
	\item[\red \xmark] $R$ is not always easy to design. 
\end{itemize}

\begin{alertblock}{Conflicting Objectives}
Complex tasks require multiple \alert{contradictory} aspects. Typically:

\begin{center}
	\Large {\green Task completion} \quad vs \quad {\red Safety}
\end{center}
\end{alertblock}
\begin{flushright}
	For example...
\end{flushright}
\end{frame}

\begin{frame}{Example problems with conflicts}
\begin{alertblock}{Dialogue systems}
A slot-filling problem: the agent fills a form by asking the user each slot. It can either:
\begin{itemize}
	\item ask to answer using {\green voice} {\green (safe/slow)};
	\item ask to answer with a {\red numeric pad} {\red (unsafe/fast)}.
\end{itemize}
\end{alertblock}
\pause
\begin{alertblock}{Autonomous Driving}
The agent is driving on a two-way road with a car in front of it,
\begin{itemize}
\item it can {\green stay behind} {\green (safe/slow)};
\item it can {\red overtake} {\red (unsafe/fast)}.
\end{itemize}
\begin{center}
\href{https://budgeted-rl.github.io/assets/highway-neutral.gif}{\includegraphics[width=0.5\linewidth]{img/highway_env}}
\end{center}
\end{alertblock}
\end{frame}

\begin{frame}{Limitation of Reinforcement Learning}
\color{gray}
Reinforcement learning relies on a single reward function $R$
\begin{itemize}
	\item[\color{gray} \checkmark] \color{gray} A convenient formulation, but;
	\item[\color{gray} \xmark] \color{gray} $R$ is not always easy to design. 
\end{itemize}

\begin{alertblock}{\color{gray}Conflicting Objectives}
	\color{gray}
	Complex tasks require multiple {contradictory} aspects. Typically:

	\begin{center}
		\Large { Task completion} \quad vs \quad { Safety}
	\end{center}
\end{alertblock}
\begin{flushright}
	For example...
\end{flushright}

\color{black}
For a fixed reward function $R$,
\begin{itemize}
	\item[\incarrow] $\pi^*$ is only guaranteed to lie on a \alert{Pareto-optimal} curve \alert{$\Pi^*$}
	\item[\incarrow] no control over the $\frac{\green \text{Task Completion}}{\red \text{Safety}}$ trade-off
\end{itemize}
\end{frame}

\begin{frame}{The Pareto-optimal curve}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto1}
\end{frame}
\begin{frame}{From maximal safety to minimal risk}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto2}
\end{frame}
\begin{frame}{The optimal policy can move freely along $\Pi^*$}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto3}
\end{frame}
\begin{frame}{How to choose a desired trade-off}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto4}
\end{frame}

@@

\begin{frame}{We want to learn $\Pi^*$ rather than $\pi^*_\beta$}
\centering
\includegraphics[width=0.9\textwidth]{img/pareto5}
\end{frame}

@@

\begin{frame}{Problem formulation}
Budgeted policies $\pi$
\begin{itemize}
	\item Take a budget $\beta$ as an additional input
	\item Output a next budget $\beta'$ 
	\item $\pi:\underbrace{(s,\beta)}_{\os} \rightarrow \underbrace{(a,\beta')}_{\oa}$
\end{itemize}
\vspace*{\baselineskip}
\begin{flushright}
		\incarrow~Augment the spaces with the budget $\beta$
\end{flushright}

@@

\begin{frame}{Scalable implementation}
